---
title: "Training and testing datasets"
author: "Esmeralda Cruz-Silva"
date: "01/04/2021"
output:
  html_document: default
  pdf_document: default
  word_document: default
---


```{r}
library(tidyverse)
```

Importing modern pollen percentages
```{r}
#   Modify path to the data
polen_path <- "/My Drive/Github_esme/Within_variability_technique/Input/Modern_pollen_percent/"
polen_name <- "Modern_pollen_percent_embsecbio_smpds_May2021.csv"
polen_file <- paste(polen_path, polen_name, sep="")
polen <- read.csv(polen_file) 

polen <- polen %>% select(-X)

str(polen)
```


Importing observed biome by using an particular search window
```{r}
#   Modify path to the data
pnv_path <- "/My Drive/Github_esme/Within_variability_technique/Input/Extract_PNV_biome/"
pnv_name <- "resolution1kmfrom250m_window21km_perside.csv"
pnv_file <- paste(pnv_path, pnv_name, sep="")
pnv_obs <- read.csv(pnv_file) 

pnv_obs <- pnv_obs %>% select(-c(Third,Third_num))

#Merging COOL with CMIX
pnv_obs$Dominant_num[pnv_obs$Dominant_num==8]<-9
pnv_obs$Dominant[pnv_obs$Dominant=="COOL"]<-"CMIX"
pnv_obs$Subdominant_num[pnv_obs$Subdominant_num==8]<-9
pnv_obs$Subdominant[pnv_obs$Subdominant=="COOL"]<-"CMIX"

str(pnv_obs)
```

#Setting some traits
```{r}
#Set path to output files
path_to_results <- "C:/Users/Esmesaurio/OneDrive - University of Reading/NEW_ITERATION_FINAL_MAY_CORECTED_2021/New_iteration_solving_downcores/R_testing/Comparison_matrices/EC4/"

#Set name of the iteration
iteration <- "EC4c_ep0.5"

#Set proportion of the data to be used as training dataset (0.7 for a training/testing ratio of 70:30)
SampFrac <- 0.7

#Set value for epsilon
EpsVal<- 0.5
```



1. Removing samples whose observed biome within the search window is NA
2. Downsampling any majoraty class to have the same size of the medium size class. In this case we downsampled any majority class towards GRAM by using Themis R package. More details in: https://themis.tidymodels.org/

```{r}
#Long format
amblong <- pnv_obs %>% 
  inner_join(polen, by="entity_name") %>% 
  subset(!is.na(Dominant)) #Remove samples whose observed biome within the search window is NA

#Wide format
ambwide_amg <- amblong %>% 
  pivot_wider(names_from = taxon_name, values_from = taxon_percent, values_fill = 0) 

#count number of samples in each biome to see the unbalance in the number of samples in each class or biome
#ambwide_amg %>% ggplot(aes(Dominant)) + geom_bar()+ geom_text(stat='count', aes(label=..count..), vjust=-0.5)

#Set a numeric value for the ratio of the majority-to-minority frequencies in each class.
ratio <- ambwide_amg %>% count(Dominant) %>% 
  mutate(med = median(n)) %>% 
  pivot_wider(names_from = Dominant, values_from = n) %>% 
  select(med,GRAM,DESE) %>%
  #mutate(ratioo = med/COOL) %>% 
  mutate(ratioo = GRAM/DESE) %>%
  select(ratioo) %>% as_vector()

#Random downsampling any majority class to have the same number of GRAM
set.seed(2468)
  recipes::recipe(~., ambwide_amg) %>%
  themis::step_downsample(Dominant, under_ratio = ratio) %>% 
  recipes::prep() %>%
  recipes::bake(new_data = NULL) -> oversamp
```


Split training and testing data
```{r}
train_data <- oversamp %>% 
  group_by(Dominant) %>% 
  sample_frac(SampFrac)

train_data %>% 
  ggplot(aes(Dominant)) +
  geom_bar()+
  geom_text(stat='count', aes(label=..count..), vjust=-0.5)

test_data <- anti_join(oversamp,train_data)

test_data %>% 
  ggplot(aes(Dominant)) +
  geom_bar()+
  geom_text(stat='count', aes(label=..count..), vjust=-0.5)
```



##Get the TRAINING data table for the algorithm
```{r}
train_data <- train_data %>% 
   pivot_longer(!c(ID_SAMPLE,entity_name,latitude,longitude,
                  Dominant,Dominant_num,Subdominant,Subdominant_num), 
               names_to = "taxon_name", values_to = "taxon_percent") %>% 
  group_by(Dominant,taxon_name) %>%
  #filter taxa that only occurs once in each group, since we cannot calculate the standard deviation
  filter(n()>=2) %>% 
  ungroup() %>%
  pivot_wider(names_from = taxon_name, values_from = taxon_percent, values_fill = 0) %>% 
  pivot_longer(!c(ID_SAMPLE,entity_name,latitude,longitude,
                  Dominant,Dominant_num,Subdominant,Subdominant_num), 
               names_to = "taxon_name", values_to = "taxon_percent") #This is the object needed for the box-plots

train_data <- train_data %>% 
  ungroup() %>% 
  group_by(Dominant, taxon_name) %>%  # Specify group indicator
  summarise_at(vars(taxon_percent),list(Mean = mean,
                                        Stdev = sd)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = Dominant, values_from = c(Mean, Stdev))


#write.csv(train_data,"./DOWNCORE/Input/BiomeData_EC4c.csv")
```


##Get the TESTING data table for the algorithm
```{r}
test_data <- test_data %>% 
  pivot_longer(!c(ID_SAMPLE,entity_name,latitude,longitude,
                  Dominant,Dominant_num,Subdominant,Subdominant_num), 
               names_to = "taxon_name", values_to = "taxon_percent") 


#Get the TESTING data table from the EMBSECBIO region
emb_test_data <- amblong %>% 
  subset(latitude>28.00000) %>% 
  subset(latitude<49.25000) %>% 
  subset(longitude>20.00000) %>% 
  subset(longitude<62.00000) %>% 
  distinct()

#write.csv(emb1,"./Input/SamplesEmbsecbio_O6.2.csv")
#rm(amblong, ambwide_amg, pnv_obs, polen)
```


# Modern biomes reconstruction using the created training and testing data
```{r}
alldata <- full_join(test_data,train_data,by="taxon_name")

#alldata <- alldata %>%
#  mutate_at(vars(-Subdominant_num,-Subdominant,-Dominant_num,-Dominant,-taxon_name,-entity_name), ~replace_na(., 0))

#str(alldata)
```



##OBSERVED DOMINANT AND SUBDOMINANT BIOMES
Get the observed dominant and subdominant biome in Hengl's PNV map for each sample
```{r}
#Get observed dominant biome
obsv_biome1 <- alldata %>% 
  filter(!is.na(ID_SAMPLE)) %>%
  dplyr::select(entity_name,ID_SAMPLE,Dominant) %>% 
  distinct() %>% group_by(entity_name)%>%
  count(Dominant) %>% 
  slice(which.max(n)) %>% 
  ungroup() %>% 
  dplyr::select(entity_name,Dominant)

#Get observed subdominant biome
obsv_biome2 <- alldata %>% 
  filter(!is.na(ID_SAMPLE)) %>%
  dplyr::select(entity_name,ID_SAMPLE,Subdominant) %>% 
  distinct() %>% group_by(entity_name)%>%
  count(Subdominant) %>% 
  slice(which.max(n)) %>% 
  ungroup() %>% 
  dplyr::select(entity_name,Subdominant)
```


##PREDICTED BIOME
Prepare the data
```{r}
#alldata <- alldata %>% 
  ##Remove taxa that are in the training set, but were not found in the testing set
 # filter(!is.na(ID_SAMPLE)) %>%
  #Remove taxa that are in the testing set, but not in the training set.
#  mutate_at(vars(a, b, c), ~replace_na(., 0))
  
 # subset(!is.na(Mean_TUND))
```


###Dissimilarity index
```{r}
sqsc <- alldata %>% 
  #Set a value for epsilon
  mutate(Epsilon=EpsVal)%>% 
  mutate(TUND_Sqrt=(taxon_percent-Mean_TUND)^2/((Stdev_TUND+Epsilon)^2)) %>% 
  mutate(DESE_Sqrt=(taxon_percent-Mean_DESE)^2/((Stdev_DESE+Epsilon)^2)) %>% 
  mutate(GRAM_Sqrt=(taxon_percent-Mean_GRAM)^2/((Stdev_GRAM+Epsilon)^2)) %>% 
  mutate(XSHB_Sqrt=(taxon_percent-Mean_XSHB)^2/((Stdev_XSHB+Epsilon)^2)) %>% 
  mutate(CENF_Sqrt=(taxon_percent-Mean_CENF)^2/((Stdev_CENF+Epsilon)^2)) %>% 
  #mutate(COOL_Sqrt=(taxon_percent-Mean_COOL)^2/((Stdev_COOL+Epsilon)^2)) %>% 
  mutate(TEDE_Sqrt=(taxon_percent-Mean_TEDE)^2/((Stdev_TEDE+Epsilon)^2)) %>% 
  mutate(CMIX_Sqrt=(taxon_percent-Mean_CMIX)^2/((Stdev_CMIX+Epsilon)^2)) %>% 
  mutate(ENWD_Sqrt=(taxon_percent-Mean_ENWD)^2/((Stdev_ENWD+Epsilon)^2)) %>% 
  mutate(WTSFS_Sqrt=(taxon_percent-Mean_WTSFS)^2/((Stdev_WTSFS+Epsilon)^2)) %>% 
  dplyr::select(ID_SAMPLE,TUND_Sqrt,DESE_Sqrt,GRAM_Sqrt,XSHB_Sqrt,CENF_Sqrt,
         TEDE_Sqrt,CMIX_Sqrt,ENWD_Sqrt,WTSFS_Sqrt) %>% 
  group_by(ID_SAMPLE) %>% 
  summarise(across(c(TUND_Sqrt,DESE_Sqrt,GRAM_Sqrt,XSHB_Sqrt,CENF_Sqrt,
         TEDE_Sqrt,CMIX_Sqrt,ENWD_Sqrt,WTSFS_Sqrt), sum))%>% 
  mutate(across(c(TUND_Sqrt,DESE_Sqrt,GRAM_Sqrt,XSHB_Sqrt,CENF_Sqrt,
         TEDE_Sqrt,CMIX_Sqrt,ENWD_Sqrt,WTSFS_Sqrt), sqrt)) %>% 
  ungroup()
```


###Get recirpocal of the scores and normalization
```{r}
biomes <- sqsc %>% 
  mutate(TUND=exp(-TUND_Sqrt)) %>% 
  mutate(DESE=exp(-DESE_Sqrt)) %>% 
  mutate(GRAM=exp(-GRAM_Sqrt)) %>% 
  mutate(XSHB=exp(-XSHB_Sqrt)) %>% 
  mutate(ENWD=exp(-ENWD_Sqrt)) %>% 
  mutate(WTSFS=exp(-WTSFS_Sqrt)) %>% 
  mutate(CENF=exp(-CENF_Sqrt)) %>% 
  #mutate(COOL=exp(-COOL_Sqrt)) %>% 
  mutate(CMIX=exp(-CMIX_Sqrt)) %>% 
  mutate(TEDE=exp(-TEDE_Sqrt)) %>%  
  dplyr::select(ID_SAMPLE,TUND,DESE,GRAM,XSHB,ENWD,
         WTSFS,CENF,CMIX,TEDE)
```



```{r}
min_max_norm <- function(x) {(x - min(x)) / (max(x) - min(x))}

biomes[2:10]<-modify(biomes[2:10],min_max_norm)
```




###Get the winner biome (highest score)
```{r}
sqsc2 <- biomes %>% 
  mutate(predicted_biome=colnames(biomes [,2:10])[apply(biomes [,2:10], 1, which.max)]) %>% 
  #mutate(predicted_num=apply(biomes [,2:11], 1, which.max)) %>% 
  dplyr::select(ID_SAMPLE,predicted_biome)
```


###Get the most common biome in entities with duplicates
```{r}
biomes <- alldata %>% 
  filter(!is.na(ID_SAMPLE)) %>%
  dplyr::select(entity_name,ID_SAMPLE) %>% 
  distinct() %>% 
  inner_join(sqsc2, by = "ID_SAMPLE") %>% 
  group_by(entity_name)%>%
  count(predicted_biome) %>% 
  slice(which.max(n)) %>% 
  ungroup() %>% 
  dplyr::select(entity_name,predicted_biome)
```


###Make a comparison table
```{r}
comparison <- biomes %>% 
  inner_join(obsv_biome1, by="entity_name") %>% 
  inner_join(obsv_biome2, by= "entity_name") %>% 
#Obtain a composit matrix
  mutate(ObsComposit = case_when(Dominant == predicted_biome ~ Dominant,
                               Subdominant == predicted_biome  ~ Subdominant)) %>% 
  mutate(ObsComposit = coalesce(ObsComposit,Dominant)) %>% 
  mutate(PredComposit = case_when(Dominant==predicted_biome ~ predicted_biome,
                                 Subdominant == predicted_biome ~ predicted_biome)) %>% 
  mutate(PredComposit = coalesce(PredComposit,predicted_biome))
```



##CONFUSION MATRIX
```{r}
observed<-ordered(comparison$Dominant,levels=c("DESE","XSHB","WTSFS","GRAM","ENWD","TEDE","CMIX","CENF","TUND"))

predicted<-ordered(comparison$predicted_biome,levels=c("DESE","XSHB","WTSFS","GRAM","ENWD","TEDE","CMIX","CENF","TUND"))

zatab<-MLmetrics::ConfusionMatrix(y_true=observed,y_pred=predicted)
zatab
  
rzatab<-round(prop.table(zatab,1)*100)
rzatab

write.csv(zatab, file=paste(path_to_results,iteration, "_Dominant.csv", sep=''))
```


```{r}
observed<-ordered(comparison$ObsComposit,levels=c("DESE","XSHB","WTSFS","GRAM","ENWD","TEDE","CMIX","CENF","TUND"))

predicted<-ordered(comparison$PredComposit,levels=c("DESE","XSHB","WTSFS","GRAM","ENWD","TEDE","CMIX","CENF","TUND"))

zatab<-MLmetrics::ConfusionMatrix(y_true=observed,y_pred=predicted)
zatab
  
rzatab<-round(prop.table(zatab,1)*100)
rzatab

write.csv(zatab, file=paste(path_to_results,iteration, "_Composit.csv", sep=''))
```




```{r}
comparison2 <- comparison %>% 
  subset(!is.na(Subdominant))

observed<-ordered(comparison2$Subdominant,levels=c("DESE","XSHB","WTSFS","GRAM","ENWD","TEDE","CMIX","CENF","TUND"))

predicted<-ordered(comparison2$predicted_biome,levels=c("DESE","XSHB","WTSFS","GRAM","ENWD","TEDE","CMIX","CENF","TUND"))

zatab<-MLmetrics::ConfusionMatrix(y_true=observed,y_pred=predicted)
#zatab
  
rzatab<-round(prop.table(zatab,1)*100)
#rzatab

write.csv(zatab, file=paste(path_to_results,iteration, "_Subdominant.csv", sep=''))
```




```{r}
comparison$predicted_biome<-as.factor(comparison$predicted_biome)
comparison$Dominant<-as.factor(comparison$Dominant)

comparison$PredComposit<-as.factor(comparison$PredComposit)
comparison$ObsComposit<-as.factor(comparison$ObsComposit)
```


Metrics calculated from the comparison matrix
```{r}
#Calculation of accuaracy
mlr3measures::acc(comparison$Dominant, comparison$predicted_biome) -> acc1
mlr3measures::acc(comparison$ObsComposit, comparison$PredComposit) -> acc2


#Calculation of balanced accuracy for a multiclass categorization (Average of recalls)
mlr3measures::bacc(comparison$Dominant, comparison$predicted_biome) -> bacc1
mlr3measures::bacc(comparison$ObsComposit, comparison$PredComposit) -> bacc2


#Create a tiny dataframe of the balance and balanced accuracy of both
metrics <- data.frame(TestData= c("WholeRegion","WholeRegion"),
                      IterEval=c("Dominant","Composit"),
                      Accuracy=c((acc1*100),(acc2*100)),
                      Balanced_accuracy=c((bacc1*100),(bacc2*100)))


#write.csv(metrics, file=paste("./Comparison matrices/EC4c_eps0.5/",iteration,"_Metrics.csv",sep=''))
```

_________________________________________________________
_________________________________________________________
_________________________________________________________
#EMBSeCBIO dataset



# Modern biomes reconstruction using the created training and testing data
```{r}
alldata <- full_join(emb_test_data,train_data,by="taxon_name")

#alldata <- alldata %>%
#  mutate_at(vars(-Subdominant_num,-Subdominant,-Dominant_num,-Dominant,-taxon_name,-entity_name), ~replace_na(., 0))
```



##OBSERVED DOMINANT AND SUBDOMINANT BIOMES
Get the observed dominant and subdominant biome in Hengl's PNV map for each sample
```{r}
#Get observed dominant biome
obsv_biome1 <- alldata %>% 
  filter(!is.na(ID_SAMPLE)) %>%
  dplyr::select(entity_name,ID_SAMPLE,Dominant) %>% 
  distinct() %>% group_by(entity_name)%>%
  count(Dominant) %>% 
  slice(which.max(n)) %>% 
  ungroup() %>% 
  dplyr::select(entity_name,Dominant)

#Get observed subdominant biome
obsv_biome2 <- alldata %>% 
  filter(!is.na(ID_SAMPLE)) %>%
  dplyr::select(entity_name,ID_SAMPLE,Subdominant) %>% 
  distinct() %>% group_by(entity_name)%>%
  count(Subdominant) %>% 
  slice(which.max(n)) %>% 
  ungroup() %>% 
  dplyr::select(entity_name,Subdominant)
```


##PREDICTED BIOME
Prepare the data
```{r}
#alldata <- alldata %>% 
  ##Remove taxa that are in the training set, but were not found in the testing set
 # filter(!is.na(ID_SAMPLE)) %>%
  #Remove taxa that are in the testing set, but not in the training set.
  #subset(!is.na(Mean_TUND))
```


###Dissimilarity index
```{r}
sqsc <- alldata %>% 
  #Set a value for epsilon
  mutate(Epsilon=EpsVal)%>% 
  mutate(TUND_Sqrt=(taxon_percent-Mean_TUND)^2/((Stdev_TUND+Epsilon)^2)) %>% 
  mutate(DESE_Sqrt=(taxon_percent-Mean_DESE)^2/((Stdev_DESE+Epsilon)^2)) %>% 
  mutate(GRAM_Sqrt=(taxon_percent-Mean_GRAM)^2/((Stdev_GRAM+Epsilon)^2)) %>% 
  mutate(XSHB_Sqrt=(taxon_percent-Mean_XSHB)^2/((Stdev_XSHB+Epsilon)^2)) %>% 
  mutate(CENF_Sqrt=(taxon_percent-Mean_CENF)^2/((Stdev_CENF+Epsilon)^2)) %>% 
  #mutate(COOL_Sqrt=(taxon_percent-Mean_COOL)^2/((Stdev_COOL+Epsilon)^2)) %>% 
  mutate(TEDE_Sqrt=(taxon_percent-Mean_TEDE)^2/((Stdev_TEDE+Epsilon)^2)) %>% 
  mutate(CMIX_Sqrt=(taxon_percent-Mean_CMIX)^2/((Stdev_CMIX+Epsilon)^2)) %>% 
  mutate(ENWD_Sqrt=(taxon_percent-Mean_ENWD)^2/((Stdev_ENWD+Epsilon)^2)) %>% 
  mutate(WTSFS_Sqrt=(taxon_percent-Mean_WTSFS)^2/((Stdev_WTSFS+Epsilon)^2)) %>% 
  dplyr::select(ID_SAMPLE,TUND_Sqrt,DESE_Sqrt,GRAM_Sqrt,XSHB_Sqrt,CENF_Sqrt,
         TEDE_Sqrt,CMIX_Sqrt,ENWD_Sqrt,WTSFS_Sqrt) %>% 
  group_by(ID_SAMPLE) %>% 
  summarise(across(c(TUND_Sqrt,DESE_Sqrt,GRAM_Sqrt,XSHB_Sqrt,CENF_Sqrt,
         TEDE_Sqrt,CMIX_Sqrt,ENWD_Sqrt,WTSFS_Sqrt), sum))%>% 
  mutate(across(c(TUND_Sqrt,DESE_Sqrt,GRAM_Sqrt,XSHB_Sqrt,CENF_Sqrt,
         TEDE_Sqrt,CMIX_Sqrt,ENWD_Sqrt,WTSFS_Sqrt), sqrt)) %>% 
  ungroup()
```


###Get recirpocal of the scores and normalization
```{r}
biomes <- sqsc %>% 
  mutate(TUND=exp(-TUND_Sqrt)) %>% 
  mutate(DESE=exp(-DESE_Sqrt)) %>% 
  mutate(GRAM=exp(-GRAM_Sqrt)) %>% 
  mutate(XSHB=exp(-XSHB_Sqrt)) %>% 
  mutate(ENWD=exp(-ENWD_Sqrt)) %>% 
  mutate(WTSFS=exp(-WTSFS_Sqrt)) %>% 
  mutate(CENF=exp(-CENF_Sqrt)) %>% 
  #mutate(COOL=exp(-COOL_Sqrt)) %>% 
  mutate(CMIX=exp(-CMIX_Sqrt)) %>% 
  mutate(TEDE=exp(-TEDE_Sqrt)) %>%  
  dplyr::select(ID_SAMPLE,TUND,DESE,GRAM,XSHB,ENWD,
         WTSFS,CENF,CMIX,TEDE)

#(alldata,"/Users/Esmesaurio/Desktop/Benja3.csv")
```



```{r}
min_max_norm <- function(x) {(x - min(x)) / (max(x) - min(x))}

biomes[2:10]<-modify(biomes[2:10],min_max_norm)
```




###Get the winner biome (highest score)
```{r}
sqsc2 <- biomes %>% 
  mutate(predicted_biome=colnames(biomes [,2:10])[apply(biomes [,2:10], 1, which.max)]) %>% 
  #mutate(predicted_num=apply(biomes [,2:11], 1, which.max)) %>% 
  dplyr::select(ID_SAMPLE,predicted_biome)
```


###Get the most common biome in entities with duplicates
```{r}
biomes <- alldata %>% 
  filter(!is.na(ID_SAMPLE)) %>%
  dplyr::select(entity_name,ID_SAMPLE) %>% 
  distinct() %>% 
  inner_join(sqsc2, by = "ID_SAMPLE") %>% 
  group_by(entity_name)%>%
  count(predicted_biome) %>% 
  slice(which.max(n)) %>% 
  ungroup() %>% 
  dplyr::select(entity_name,predicted_biome)
```


###Make a comparison table
```{r}
comparison <- biomes %>% 
  inner_join(obsv_biome1, by="entity_name") %>% 
  inner_join(obsv_biome2, by= "entity_name") %>% 
#Obtain a composit matrix
  mutate(ObsComposit = case_when(Dominant == predicted_biome ~ Dominant,
                               Subdominant == predicted_biome  ~ Subdominant)) %>% 
  mutate(ObsComposit = coalesce(ObsComposit,Dominant)) %>% 
  mutate(PredComposit = case_when(Dominant==predicted_biome ~ predicted_biome,
                                 Subdominant == predicted_biome ~ predicted_biome)) %>% 
  mutate(PredComposit = coalesce(PredComposit,predicted_biome))
```



##CONFUSION MATRIX
```{r}
observed<-ordered(comparison$Dominant,levels=c("DESE","XSHB","WTSFS","GRAM","ENWD","TEDE","CMIX","CENF","TUND"))

predicted<-ordered(comparison$predicted_biome,levels=c("DESE","XSHB","WTSFS","GRAM","ENWD","TEDE","CMIX","CENF","TUND"))

zatab<-MLmetrics::ConfusionMatrix(y_true=observed,y_pred=predicted)
zatab
  
rzatab<-round(prop.table(zatab,1)*100)
rzatab

write.csv(zatab, file=paste(path_to_results,iteration, "_EMB_Dominant.csv", sep=''))
```


```{r}
observed<-ordered(comparison$ObsComposit,levels=c("DESE","XSHB","WTSFS","GRAM","ENWD","TEDE","CMIX","CENF","TUND"))

predicted<-ordered(comparison$PredComposit,levels=c("DESE","XSHB","WTSFS","GRAM","ENWD","TEDE","CMIX","CENF","TUND"))

zatab<-MLmetrics::ConfusionMatrix(y_true=observed,y_pred=predicted)
zatab
  
rzatab<-round(prop.table(zatab,1)*100)
rzatab

write.csv(zatab, file=paste(path_to_results,iteration, "_EMB_Composit.csv", sep=''))
```


```{r}
comparison2 <- comparison %>% 
  subset(!is.na(Subdominant))

observed<-ordered(comparison2$Subdominant,levels=c("DESE","XSHB","WTSFS","GRAM","ENWD","TEDE","CMIX","CENF","TUND"))

predicted<-ordered(comparison2$predicted_biome,levels=c("DESE","XSHB","WTSFS","GRAM","ENWD","TEDE","CMIX","CENF","TUND"))

zatab<-MLmetrics::ConfusionMatrix(y_true=observed,y_pred=predicted)
#zatab
  
rzatab<-round(prop.table(zatab,1)*100)
#rzatab

write.csv(zatab, file=paste(path_to_results,iteration, "_EMB_Subdominant.csv", sep=''))
```




```{r}
comparison %>% 
  filter(!predicted_biome%in%c("TUND","CENF")) %>% 
  filter(!Dominant%in%c("TUND","CENF"))->comparison


comparison$predicted_biome<-as.factor(comparison$predicted_biome)
comparison$Dominant<-as.factor(comparison$Dominant)

comparison$PredComposit<-as.factor(comparison$PredComposit)
comparison$ObsComposit<-as.factor(comparison$ObsComposit)
```


Metrics calculated from the comparison matrix
```{r}
#Calculation of accuaracy
mlr3measures::acc(comparison$Dominant, comparison$predicted_biome) -> acc1
mlr3measures::acc(comparison$ObsComposit, comparison$PredComposit) -> acc2


#Calculation of balanced accuracy for a multiclass categorization (Average of recalls)
mlr3measures::bacc(comparison$Dominant, comparison$predicted_biome) -> bacc1
mlr3measures::bacc(comparison$ObsComposit, comparison$PredComposit) -> bacc2


#Create a tiny dataframe of the balance and balanced accuracy of both
metrics2 <- data.frame(TestData= c("EMBSE","EMBSE"),
                       IterEval=c("Dominant","Composit"),
                       Accuracy=c((acc1*100),(acc2*100)),
                       Balanced_accuracy=c((bacc1*100),(bacc2*100)))


#write.csv(metrics2, file=paste("./Comparison matrices/EC4c_eps0.5/",iteration,"_EMB_Metrics.csv",sep=''))
```



```{r}
metrics_final <- bind_rows(metrics,metrics2)

metrics_final

write.csv(zatab, file=paste(path_to_results,iteration, "_Metrics.csv", sep=''))
```

